\herschel\footnote{{\it Herschel} is an ESA space observatory with science instruments provided by European-led Principal Investigator consortia and with important participation from NASA.} Orion Protostar Survey (HOPS) Imaging and Photometry Results.

### 2017-04-29 HOPS/photometry/ms.tex
figure captions table numbers fixed

Unfortunately, this strong link to their surrounding environment also makes protostars difficult to study.  In particular:  (i) observational studies must be able to disentangle the degenerate effects of both the environment and the star-formation process itself.  Protostars are characterized by a central core, an accretion disk, outflows, and an infalling envelope \citep{ali}. Additionally, protostars alter their local environment with phenomenon such as Herbig-Haro objects \citep{hhobjects}.  The spatial scales for all of these components range from less than 1 AU to 100s of AUs \citep{mo07}.  Thus, observational strategies must account for this compact, yet complicated morphology.  Further, (ii) the presence of dust in the local environment means the amount of extinction in lines-of-sight to star formation regions is abnormally high (few to several tens of magnitudes in the visual) compared to most of the rest of the Galaxy \citep{dobbs}.  Finally, (iii)  \spitzer\ and \herschel\ observations, in particular, confirmed long recognized views that far-IR observations of the reprocessed radiation can probe the evolution of protostars \citep{als87}.  The presence of an infalling envelope of gas and dust is a defining characteristic of protostars. This envelope absorbs the radiation from the central accreting star+disk and reprocesses most of the luminosity into the far-IR \citep{ali}.   Far-IR observations are, therefore, absolutely crucial for efficiently identifying and studying protostars because protostars emit most of their light at those wavelengths.

@@

Second, we focus on the nearby star-forming region Orion \citep{orion}.  Orion provides several key advantages.  \cite{orion} identified a rich sample of protostars in Orion from \spitzer\ thus providing us a collection of protostars in a variety of environmental conditions.  Star formation has been observed in a rich diversity of environments, from isolated cold globules to rich clusters. See, for example, \cite{carpenter}, \cite{feigelson}, \cite{amy2010}.   Also, at 419 pc \citep{schlafly} , Orion is relatively nearby and, thus, allows relatively high spatial resolution to resolve morphologies.

@@

\begin{deluxetable}{lrrc}
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{The sub-region boundaries (in decimal degrees) for the Orion A~\&~B clouds\label{tbl:regions}}
\tablehead{
\colhead{Name} &
\multicolumn{2}{c}{Declination Boundary} &
\colhead{Number of protostars} \\
\colhead{}&
\colhead{Low} &
\colhead{High} &
\colhead{}
}
\startdata
LDN 1622     & 1.3     & 2.08   & 11\\
NGC 2068    & -0.5   & 1.3     & 59 \\
NGC 2023/4 & -3.83 & -0.5   & 27\\
OMC 2/3       & -5.3 & -3.83 & 64\\
ONC-S          & -6.1 & -5.3 & 54\\
LDN 1641-N & -6.9 & -6.1 & 47\\
LDN 1641-C & -7.6 & -6.9 & 62\\
LDN 1641-S & -9      & -7.6 & 85\\
\enddata
\end{deluxetable}

@@

\begin{figure*}[ht]
\centering
\includegraphics[height=5in]{figures/LFs.eps}
\caption{Flux distributions at 70~\micron\ (top, blue) and 160~\micron\ (bottom, red) for all sources in the HOPS sample.  The upper limits are not used to calculate the distribution.\label{fig:fd}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plotone{figures/num_vs_dec.eps}
\caption{Number of protostars as a function of sub-region in Orion.\label{fig:num_v_dec}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plotone{figures/f70_v_clr2.eps}
\caption{The observed 70~\micron\ flux as a function of the \clra\ (left) and \clrb\ (right) flux ratios.\label{fig:clrflux}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plotone{figures/clr_vs_flimit.eps}
\caption{The observed mean color above the simulated completeness limit for LDN~1641.  Solid lines show the mean values for \clra\ (black) and \clrb\ (blue) with limiting flux.  The dashed lines show the mean color for the combined Orion ONC and OMC-2/3 region.  As discussed in text, we note a complete lack of correlation between the completeness limit and mean color for \clrb.  We note a steady increase in the mean \clra as a function of the completeness limit.  However, the average completeness limits require significant differences before the LDN 1641 sub0region can be explained as being similar to Orion OMC-2/3 and the ONC.\label{fig:clr_v_limit}}
\end{figure*}

@@

\bibitem[Fischer \etal\ (2016)]{will} Fischer, W., J., \etal, 2017 submitted

@@

\bibitem[]{hhobjects} O'dell, C., R., Hartigan, P., Lane, W., M., Wong, S., K., Burton, M., G., Raymond, J., \& Axon, D., 1997, AJ, 114, 730

>>>>

Unfortunately, this strong link to their surroundings also makes protostars difficult to study.  In particular:  (i) observational studies must be able to disentangle the degenerate effects of both the environment and the star-formation process itself.  Protostars are characterized by a central core, an accretion disk, outflows, and an infalling envelope \citep{ali}. Additionally, protostars alter their local environment with phenomenon such as Herbig-Haro objects \citep{hhobjects}.  The spatial scales for all of these components range from less than 1 AU to 100s of AUs \citep{mo07}.  Thus, observational strategies must account for this compact, yet complicated morphology.  Further, (ii) the presence of dust in the local environment means the amount of extinction in lines-of-sight to star formation regions is abnormally high (few to several tens of magnitudes in the visual) compared to most of the rest of the Galaxy \citep{dobbs}.  Finally, (iii)  \spitzer\ and \herschel\ observations, in particular, confirmed long recognized views that far-IR observations of the reprocessed radiation can probe the evolution of protostars \citep{als87}.  The presence of an infalling envelope of gas and dust is a defining characteristic of protostars. This envelope absorbs the radiation from the central accreting star+disk and reprocesses most of the luminosity into the far-IR \citep{ali}.   Far-IR observations are, therefore, absolutely crucial for efficiently identifying and studying protostars because protostars emit most of their light at those wavelengths.

@@

Second, we focus on the nearby star-forming region, Orion \citep{orion}.  Orion provides several key advantages.  \cite{orion} identified a rich sample of protostars in Orion from \spitzer\ thus providing us a collection of protostars in a variety of environmental conditions.  Star formation has been observed in a rich diversity of environments, from isolated cold globules to rich clusters. See, for example, \cite{carpenter}, \cite{feigelson}, \cite{amy2010}.   Also, at 419 pc \citep{schlafly} , Orion is relatively nearby and, thus, allows relatively high spatial resolution to resolve morphologies.

@@

\begin{deluxetable}{lrrc}
\tablecolumns{4}
\tablewidth{0pt}
\tablenum{2}
\tablecaption{The sub-region boundaries (in decimal degrees) for the Orion A~\&~B clouds\label{tbl:regions}}
\tablehead{
\colhead{Name} &
\multicolumn{2}{c}{Declination Boundary} &
\colhead{Number of protostars} \\
\colhead{}&
\colhead{Low} &
\colhead{High} &
\colhead{}
}
\startdata
LDN 1622     & 1.3     & 2.08   & 11\\
NGC 2068    & -0.5   & 1.3     & 59 \\
NGC 2023/4 & -3.83 & -0.5   & 27\\
OMC 2/3       & -5.3 & -3.83 & 64\\
ONC-S          & -6.1 & -5.3 & 54\\
LDN 1641-N & -6.9 & -6.1 & 47\\
LDN 1641-C & -7.6 & -6.9 & 62\\
LDN 1641-S & -9      & -7.6 & 85\\
\enddata
\end{deluxetable}

@@

\begin{figure*}[ht]
\centering
\includegraphics[height=5in]{figures/LFs.eps}
\caption{Flux distributions at 70~\micron\ (top, blue) and 160~\micron\ (bottom, red) for all sources in the HOPS sample.  Only sources with actual measurements are shown.  The upper limits are not used.\label{fig:fd}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plotone{figures/num_vs_dec.eps}
\caption{The number of protostars as a function of sub-region in Orion.\label{fig:num_v_dec}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plotone{figures/f70_v_clr2.eps}
\caption{Flux density vs log flux ratio diagrams for Orion.  (left) The observed 70~\micron\ flux as a function of the \clra\ , and \clrb\ (right) flux ratios.\label{fig:clrflux}}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\plotone{figures/clr_vs_flimit.eps}
\caption{Completion limit as an explanation for observed color differences in the Orion sub-regions.  The observed mean color above the artificially imposed completeness limit for LDN~1641.  Solid lines show the mean values for \clra\ (blue) and \clrb\ (red) with the chosen limiting flux.  The dashed lines show the mean color for the combined Orion ONC and OMC-2/3 region.  As discussed in text, we note a complete lack of correlation between the artificially imposed completeness limit and mean color for \clrb.  We note a steady increase in the mean \clra as a function of the completeness limit.  Differences in \clra\ between LDN-1641 and Orion OMC-2/3 + ONC can be explained as difference in completions limits.  However, completion limit differences cannot explain the color differences for \clrb\ in these simulations for the sub-regions.\label{fig:clr_v_limit}}
\end{figure*}

@@

\bibitem[Fischer \etal\ (2017)]{will} Fischer, W., J., \etal, 2017, ApJ, accepted for publication.

@@

\bibitem[O'Dell \etal\ (1997)]{hhobjects} O'Dell, C., R., Hartigan, P., Lane, W., M., Wong, S., K., Burton, M., G., Raymond, J., \& Axon, D., 1997, AJ, 114, 730
